---
title: "Regression Data BA"
author: "Niklas Bacher"
date: "2023-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Load packages and import prepared data from Python

```{r, message=FALSE}
pacman::p_load(tidyverse, stargazer, nnet, extrafont, thematic, effects, car, reshape2)
loadfonts()
```

```{r}
reg_data <- read.csv("regression_data.csv")
```

```{r}
reg_data <- reg_data %>%
  mutate(type_of_violence = as.factor(type_of_violence),
         type_of_violence = relevel(type_of_violence, ref = "one-sided"),
         fatalities_log = log(fatalities),
         year = as.factor(year),
         country = as.factor(country)) %>% 
  filter(!country %in% c("CPV","COM", "MUS", "STP","SYC"))# Filter Island Nations
```



### Model 1 - 2 (Fatalities on remoteness)

```{r}
h1_data <- reg_data %>% 
  filter(fatalities > 0)
```

```{r}
model1 <- lm(fatalities_log ~ remoteness_nat, data = h1_data)
#summary(model1)

model2 <- lm(fatalities_log ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + country + year, data = h1_data)

#summary(model2)
```

```{r warning=FALSE}
#stargazer(model1, model2, title = "Regression output for Hypothesis 1", model.names = TRUE, omit = c("country", "year"))
```



### Model 3 - 4 (type of violence on remoteness (Multinomial Logistic Regression))

```{r}
h2_data <- reg_data %>% 
  filter(fatalities > 0)
```

```{r}
model3 <- multinom(type_of_violence ~ remoteness_nat, data = h2_data)
#summary(model3)

model4 <- multinom(type_of_violence ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = h2_data)
#summary(model4)
```

```{r}
#stargazer(model3, model4, title = "Regression output for Hypothesis 2",  omit = c("country", "year"))
```

```{r}
coefficients_model3 <- coef(model3)
selected_coefficients_model3 <- coefficients_model3[1:2,2]
odds_ratios_model3 <- exp(selected_coefficients_model3)
odds_ratios_model3

coefficients_model4 <- coef(model4)
selected_coefficients_model4 <- coefficients_model4[1:2,2]
odds_ratios_model4 <- exp(selected_coefficients_model4)
odds_ratios_model4
```



### Model 5 - 6 (Fatalities on type of conflict)

```{r}
h3_data <- reg_data %>% 
  filter(fatalities > 0)
```

```{r}
model5 <- lm(fatalities_log ~ type_of_violence, data = h3_data)
#summary(model5)

model6 <- lm(fatalities_log ~ type_of_violence + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = h3_data)
#summary(model6)
```

```{r warning=FALSE}
#stargazer(model5, model6, title = "Regression output for Hypothesis 3",  omit = c("country", "year"))
```



### Descriptive Statistics

```{r}
# Descripitve Statistics Table
descriptive_data <- reg_data %>% 
  select(fatalities, remoteness_nat, remoteness_reg, mountains_mean, bdist2, nlights_calib_mean, excluded)

#stargazer(descriptive_data, type = "latex",
    #     summary.stat = c("n", "mean", "median", "min", "max"),
       #   title = "Descriptive Statistics")
```
`

```{r message=FALSE}
# Linegraph - Conflicts per year by conflict
aggregate_data <- reg_data %>%
  group_by(year, type_of_violence) %>%
  summarise(conflicts_count = n(), .groups = 'drop')

ggplot(aggregate_data, aes(x = year, y = conflicts_count, group = type_of_violence, color = type_of_violence)) +
  geom_line(linewidth = 1) +
  theme_minimal(base_size = 12,
                base_family = "LM Roman 10") +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.5, linetype = 2),
    plot.title.position = "plot",
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(face = 'bold')
  ) + 
  labs(title = "Number of conflicts per year grouped by conflict type",
       x = "Year",
       y = element_blank(),
       color = "Conflict Type",
       caption = "Source: UCDP GED") +
  scale_color_manual(values = thematic::okabe_ito(3))
```

```{r}
# Barchart - Top 10 countries
aggregate_data <- reg_data %>%
  group_by(country) %>%
  summarise(conflicts_count = n(), .groups = 'drop') %>% 
  filter(conflicts_count > 2000) %>% 
  arrange(conflicts_count) %>% 
  mutate(country = factor(country, levels = country)) 

ggplot(aggregate_data, aes(x = conflicts_count, y = country)) +
  geom_col(fill = thematic::okabe_ito(1)) +
  geom_text(
    aes(label = conflicts_count),hjust = 1.15, size = 3, color = "white"
  ) +
  theme_minimal(
    base_family = "LM Roman 10"
  ) +
  labs(
    x = element_blank(),
    y = element_blank(),
    title = 'The 10 most conflict-affected countries in Africa between 1989 and 2022'
  ) +
  theme(
    panel.grid = element_blank(),
    plot.title.position = 'plot',
    axis.text.y = element_text(face = 'bold', size = 11)
  ) +
  scale_x_continuous(
    breaks = NULL,
    expand = expansion(mult = c(0,0.01))
  ) 

```


```{r}
# Test in wie vielen Ländern keine Konflikte passiert sind
unique_countries_reg_data <- unique(reg_data$GID_0)
all_countries_africa <- c('DZA', 'AGO', 'BEN', 'BWA', 'BFA', 'BDI', 'CPV', 'CMR', 'CAF', 'TCD', 'COM', 'COD', 'COG', 'CIV', 'DJI', 'EGY', 'GNQ', 'ERI', 'SWZ', 'ETH', 'GAB', 'GMB', 'GHA', 'GIN', 'GNB', 'KEN', 'LSO', 'LBR', 'LBY', 'MDG', 'MWI', 'MLI', 'MRT', 'MUS', 'MAR', 'MOZ', 'NAM', 'NER', 'NGA', 'RWA', 'STP', 'SEN', 'SYC', 'SLE', 'SOM', 'ZAF', 'SSD', 'SDN', 'TZA', 'TGO', 'TUN', 'UGA', 'ZMB', 'ZWE')

setdiff(all_countries_africa, unique_countries_reg_data)
```
CPV: Kap Verde
COM: Komoren
EGY: Ägypten
GNQ: Äquatorialguinea
GAB: Gabun
MDG: Madagaskar
MWI: Malawi
MUS: Mauritius
STP: São Tomé und Príncipe
SYC: Seychellen



### Basic Assumption Tests

```{r}
test_data <- reg_data %>% 
  filter(fatalities > 0)
```

```{r}
# Variance Inflation Factor
test_model <- lm(fatalities_log ~ remoteness_nat + + type_of_violence + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = test_data)

vif(test_model)
```

```{r}
# Outlier Check
test_data_melted <- test_data %>% 
  mutate("Travel time to capital" = log(remoteness_nat),
         "Distance to border" = log(bdist2),
         "Nighttime light" = log(nlights_calib_mean)) %>% 
  rename("Fatalities (log)" = fatalities_log,
         "Mountainous %" = mountains_mean,
         "Excluded ethnic groups" = excluded) %>%
   select("Fatalities (log)","Travel time to capital","Distance to border","Nighttime light","Fatalities (log)","Mountainous %","Excluded ethnic groups") %>% 
  melt()

ggplot(test_data_melted, aes(y=variable, x=value)) +
  geom_boxplot() +
  facet_wrap(~ variable, scales = "free") +
  theme_minimal(
    base_family = "LM Roman 10"
  ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        axis.text.y = element_text(face = 'bold', size = 11),
        strip.text = element_blank()) +
  labs(x = element_blank(),
         y = element_blank())

```

```{r}
# IIA Assumption
alt_model1_data <- test_data %>% 
  filter(type_of_violence != "state-based")

alt_model2_data <- test_data %>% 
  filter(type_of_violence != "non-state")

alt_model3_data <- test_data %>% 
  filter(type_of_violence != "one-sided")


#iaa_model1 <- multinom(type_of_violence ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = alt_model1_data)

#iaa_model2 <- multinom(type_of_violence ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = alt_model2_data)

#iaa_model3 <- multinom(type_of_violence ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = alt_model3_data)

#stargazer(iaa_model1,iaa_model2,iaa_model3, title = "Regression output for constrained models veryfing IAA assumption",  omit = c("country", "year"))
```



### Robustness Tests

```{r}
logit_data <- reg_data %>% 
  filter(fatalities > 0) %>% 
  mutate(state_based = ifelse(type_of_violence == "state-based", 1, 0),
         one_sided = ifelse(type_of_violence == "one-sided", 1, 0),
         non_state = ifelse(type_of_violence == "non-state", 1, 0))
```

```{r}
# Robustness Model with dichotomous conflict type instead of MLM
model_state_based <- glm(state_based ~ remoteness_nat, data = logit_data, family = binomial(link = "logit"))
#summary(model_state_based)

model_state_based_control <- glm(state_based ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = logit_data, family = binomial(link = "logit"))
#summary(model_state_based_control)

#stargazer(model_state_based, model_state_based_control, title = "Regression output for dichotomous conflict type variable",  omit = c("country", "year"), type = "text")
```

```{r}
# Robustness Model with excluded extreme violent events to mitigate skewed distribution

threshhold <- quantile(reg_data$fatalities, 0.99)

bottom_99 <- reg_data %>% 
  filter(fatalities < threshhold,
         fatalities > 0)

model_bottom99_h1 <- lm(fatalities_log ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = bottom_90)
#summary(model_bottom99_h1)

model_bottom90_h2 <- multinom(type_of_violence ~ remoteness_nat + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = bottom_90)
#summary(model_bottom90_h2)

model_bottom90_h3 <- lm(fatalities_log ~ type_of_violence + mountains_mean + bdist2 + nlights_calib_mean + excluded + year + country, data = bottom_90)
#summary(model_bottom90_h3)

#stargazer(model_bottom99_h1, model_bottom90_h3, model_bottom90_h2, title = "Regression Output Excluding the Top 1% Deadliest Conflict Events",  omit = c("country", "year"))
```


